### 2024-05-10 README.Rmd
Run man, run man, run.

## Example

```{r example}
library(traveltime)
library(terra)

@@

```{r}
plot(friction_surface)
```

```{r}
from_here <- tibble::tibble(
  x = c(111.2, 111.9),
  y = c(0.2, 0.35)
)
from_here
```

```{r}
travel_time <- calculate_travel_time(
  friction_surface = friction_surface,
  points = from_here
)
travel_time
```

```{r}
plot(travel_time)
points(from_here, pch = 19, add = TRUE)
```

>>>>

## Let's calculate some travel times

First download a friction surface — here using the motorised travel time from
Weiss *et al.* 2020.
```{r example}
library(traveltime)
library(terra)

@@

Let's have a look at that
```{r}
plot(friction_surface)
```

Prepare points we would like to calculate travel time from
```{r}
from_here <- tibble::tibble(
  x = c(111.2, 111.9),
  y = c(0.2, 0.35)
)
from_here
```

And calculate the travel time
```{r}
travel_time <- calculate_travel_time(
  friction_surface = friction_surface,
  points = from_here
)
travel_time
```

Et voila!
```{r}
plot(travel_time)
points(from_here, pch = 19, add = TRUE)
```
